Model_CFU

### 2017-01-09 code/HumanCdGF_cdiff_colonization.Rmd
pull dist generated dist in mothur into R

#homova(phylip=~/Desktop/day_0_communities.thetayc.0.03.lt.ave.dist, design=~/Desktop/day_0_communities.CL.design)
HOMOVA	BValue	P-value	SSwithin/(Ni-1)_values
hi-lo-mid	21.6225	<0.001*	0.000145266	0.0966271	0.370517
hi-lo	14.1638	<0.001*	0.000145266	0.0966271
hi-mid	18.2515	<0.001*	0.000145266	0.370517
lo-mid	3.48295	<0.001*	0.0966271	0.370517
# all groups have significantly different variation (hi = 0.0001, mid = 0.37, lo = 0.097)

dist_cl <- vegdist(nmds_df[,-c(1,2)])
nmds <- metaMDS(nmds_df[,-c(1:2)])
stressplot(nmds, dist_cl)
plot(nmds, type = 'n')
points(nmds, display = 'sites', pch = 21, bg = as.numeric(as.factor(nmds_df$human_source)))
#text(nmds, display = 'species', cex = 0.5)
envfit(nmds ~ )
```

>>>>

#homova(phylip=~/Desktop/day_0_communities.thetayc.0.03.lt.ave.dist, design=~/Desktop/day_0_communities.CL.design)
HOMOVA	BValue	P-value	SSwithin/(Ni-1)_values
hi-lo-mid	21.6225	<0.001*	0.000145266	0.0966271	0.370517
hi-lo	14.1638	<0.001*	0.000145266	0.0966271
hi-mid	18.2515	<0.001*	0.000145266	0.370517
lo-mid	3.48295	<0.001*	0.0966271	0.370517
# all groups have significantly different variation (hi = 0.0001, mid = 0.37, lo = 0.097)
```

```{r NMDS of Colonization Level}

full_shared_file <- 'data/process/full_shared.shared'
full_shared_file <- read.table(full_shared_file, sep = '\t', header = T)

dist_file <- 'data/process/nmds_colonization_level/day_0_communities.thetayc.0.03.lt.ave.dist'
dist_day_0_comm <- scan(dist_file, what = 'character') # load dist file as vector
n_samples_dist <- as.numeric(dist_day_0_comm[1]) # save sample number and remove from dist vector
dist_day_0_comm <- dist_day_0_comm[-1]
dist_matrix <- data.frame(matrix(NA, nrow = n_samples_dist, ncol = n_samples_dist)) # matrix size of samples
diag_value <- 0
diag(dist_matrix) <- diag_value # fills in diagonal
c <- 1 # c keep track of position in dist vector
for(i in 1:n_samples_dist){
  sample <- dist_day_0_comm[c]
  colnames(dist_matrix)[i] <- sample
  rownames(dist_matrix)[i] <- sample
  if(i > 1){
    dist_matrix[i,1:(i-1)] <- dist_day_0_comm[(c+1):(c+i-1)] # fill in matrix
  }
  c <- c+i # maintain position in dist vector
}
dist_matrix[upper.tri(dist_matrix)] <- t(dist_matrix)[upper.tri(dist_matrix)] #fill in upper triangle

nmds <- metaMDS(dist_matrix)
stressplot(nmds)
plot(nmds, type = 'n')

#points(nmds, display = 'sites', pch = 21, bg = as.numeric(as.factor(nmds_df$human_source)))
#text(nmds, display = 'species', cex = 0.5)
#envfit(nmds ~ )
```
